title: "DifferentState"
author: "Kaiyan Li"
date: "19/11/2020"
output: pdf_document
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyverse)
```

##Data Cleaning
```{r}
cdc = read.csv("Nutrition__Physical_Activity__and_Obesity_-_Behavioral_Risk_Factor_Surveillance_System.csv")
# Removing LocationAbbr, and renaming LocationDesc
cdc_adjusted = cdc %>% select(-YearEnd) %>% rename(Year = YearStart)
cdc_adjusted = cdc_adjusted %>% select(-LocationAbbr) %>% rename(Location = LocationDesc)
# Removing DataSource, Topic, TopicID, ClassID, QuestionID, GeoLocation, Data_Value_Unit, 
# Data_Value_Type, DataValueTypeID
cdc_adjusted = cdc_adjusted %>% select(-Datasource, -Topic, -TopicID, -ClassID, -QuestionID, -GeoLocation, -Data_Value_Unit, -Data_Value_Type, - DataValueTypeID)
# Removing more variables... Data_Value_Footnote_Symbol, StratificationCategoryId1, StratificationID1
cdc_adjusted = cdc_adjusted %>% select(-Data_Value_Footnote_Symbol, -StratificationCategoryId1, -StratificationID1)
#Also going to remove Data_Value_Foot_Note, Low CL, High CL
cdc_adjusted = cdc_adjusted %>% select(-Data_Value_Alt, -Data_Value_Footnote, -Low_Confidence_Limit, -High_Confidence_Limit  )
```
##End of Data Cleaning

####################################################################################

## Test which states have obesity percentage increase over the years
```{r}
#Filter out Question == "Percent of adults aged 18 years and older who have obesity" & Total == 'Total'
total_obesity = cdc_adjusted %>% filter(Question == "Percent of adults aged 18 years and older who have obesity" & Total == 'Total')
n=max(total_obesity$LocationID)
beta1=rep(NA,n)
pvalue = rep(NA,n)
for (i in c(1:n)){
  subset = total_obesity %>% filter(LocationID == i)
  if (nrow(subset) >= 3){
    state_model = lm(Data_Value ~ Year, data=subset)
    beta1[i] = coef(summary(state_model))[2,1]
    pvalue[i] = coef(summary(state_model))[2,4]
  }
}
#Find which states have p-values < 0.05 
which(pvalue<0.05)
#Whether those states have positive beta_1
beta1[c(which(pvalue<0.05))]
